---
title: "Healthcare System Meta-data"
author: "Meg Hutch"
date: "2022-11-01"
output: html_document
---

This notebook organizes each participating healthcare system's data to abstract the date up to which patients were admitted. Additionally, we generate a table of each site's adult, pediatric, and total patient counts.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(kableExtra)
```

## **Import Data from each Healthcare System**

```{r message=FALSE, warning=FALSE}
# read in files from results folder 
# this folder contains all of the local healthcare system level analyses
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}

rm(rdas, rda)

# create a list of participating healthcare systems from our study tracking spreadsheet
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"

# load site parameters
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

# filter the list of sites who ran the analysis
sorted_sites <- site_avails %>%
  filter(!is.na(date_v4_received)) %>%
  pull(siteid) %>%
  paste("results", sep = "_")

# list sites without race
sites_wo_race <- site_params %>%
  filter(!include_race) %>%
  pull(siteid)

# combine all rda files with 'results' in name
results <- mget(ls(pattern = "results"))
```

### **Latest Admission Date**

The generated table shows the latest month-year that a healthcare system include patients for the analysis.

```{r}
adm_date_list <- list()

for (i in sorted_sites) {
  #print(i)
  tmp <- get(i)
  adm_date_table <- tmp[["site_last_admission_date"]]

  adm_date_list[[i]] <- adm_date_table 
  
}

adm_date_df <- bind_rows(adm_date_list) %>% 
  t() %>% 
  data.frame() %>% 
  rename(site_last_admission_date = '.') %>% 
  mutate(site_last_admission_date = gsub("-", "-01-", site_last_admission_date),
         site_last_admission_date = as.Date(site_last_admission_date, format = '%m-%d-%Y'))

datatable(adm_date_df)
```

### **Patient Counts**

```{r message=FALSE, warning=FALSE}
pt_counts_list <- list()


for (i in sorted_sites) {
  #print(i)
  tmp <- get(i)
  
  try(  
  adult <- tmp[["first_hosp_results"]][["tableone_results"]][["tableone_adults"]][["demo_table"]] %>% 
    # use 'sex' to calculate total counts (less likely to be masked from stratification of smaller numbers such as would be the case if we chose 'age_group')
    filter(grepl('sex', variable)) %>% 
    select(contains('n_var')) %>% 
    summarise_all(., ~ sum(.x)) %>% 
    mutate(population = 'Adult',
           site = paste(i)) %>% 
    select(site, population, everything()),
  silent = TRUE
  )
  
  try(  
  pediatric <- tmp[["first_hosp_results"]][["tableone_results"]][["tableone_pediatrics"]][["demo_table"]] %>% 
    # use 'sex' to calculate total counts (less likely to be masked from stratification of smaller numbers such as would be the case if we chose 'age_group')
    filter(grepl('sex', variable)) %>% 
    select(contains('n_var')) %>% 
    summarise_all(., ~ sum(.x)) %>% 
    mutate(population = 'Pediatric',
           site = paste(i)) %>% 
    select(site, population, everything()), 
  silent = TRUE
  )

  pt_counts_list[[i]] <- bind_rows(adult, pediatric)
  
}

# remove BCH adult counts - we are excluding these patients from the meta-analysis
pt_counts_df <- bind_rows(pt_counts_list) %>% 
  filter(!(site == "BCH_results" & population == "Adult")) %>% 
  replace(is.na(.), 0) %>% 
  distinct() %>% 
  mutate(total_population = rowSums(select(., contains("n_var")), na.rm = TRUE)) %>% 
  # calculate total (adult + pediatric)
  group_by(site) %>% 
  mutate(total_adult_peds = sum(total_population, na.rm = TRUE)) %>% 
  ungroup()
  
  
datatable(pt_counts_df)
```

**Save Patient Counts**

```{r}
write.csv(pt_counts_df, 'tables/site_pt_counts.csv', row.names = FALSE)
```


