---
title: "Comorbidity Pre-processing"
author: "Meg Hutch"
date: "2022-11-16"
output: html_document
---

Pre-process comorbidity data for use in downstream analysis.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
```

# **Import Data from each Healthcare system**

```{r message=FALSE, warning=FALSE}
# read in files from results folder 
# this folder contains all of the local healthcare system level analyses
rdas <- list.files(
  path = "results_comorbidity",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}

rm(rdas, rda)

# create a list of participating healthcare systems from our study tracking spreadsheet
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"

# load site parameters
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

# filter the list of sites who ran the analysis
sorted_sites <- site_avails %>%
  filter(comorb_results == "completed") %>%
  pull(siteid) %>%
  paste("comorb_results", sep = "_")

# combine all rda files with 'results' in name
results_comorbidities <- mget(ls(pattern = "results"))

comorb_results <- list()

for(i in sorted_sites) {
    
    tmp <- get(i)
    comorb <- tmp[[c(
      "first_hosp_results",
      "tableone_comorbidity_results"
    )]]
    
    comorb_results[[i]] <- comorb
}
```

## **Prepare list of Elixhuaser comorbidities**

First, we will create a list of comorbidities, which will help us deal with data cleaning issues.

Comorbidity list obtained from [icd](https://github.com/jackwasey/icd) package icd/data/mappingNames, which was used to calculate the Elixhauser comorbidity score in the analysis

```{r}
# HTN marked together as combined, but DM not.
names_elix_htn <- list(
  "01" = "Congestive heart failure",
  "02" = "Cardiac arrhythmias",
  "03" = "Valvular disease",
  "04" = "Pulmonary circulation disorders",
  "05" = "Peripheral vascular disorders",
  "06a" = "Hypertension, uncomplicated",
  "06b" = "Hypertension, complicated",
  "07" = "Paralysis",
  "08" = "Other neurological disorders",
  "09" = "Chronic pulmonary disease",
  "10" = "Diabetes, uncomplicated",
  "11" = "Diabetes, complicated",
  "12" = "Hypothyroidism",
  "13" = "Renal failure",
  "14" = "Liver disease",
  "15" = "Peptic ulcer disease excluding bleeding",
  "16" = "HIV/AIDS",
  "17" = "Lymphoma",
  "18" = "Metastatic cancer",
  "19" = "Solid tumor without metastasis",
  "20" = "Rheumatoid arthritis/collagen vascular diseases",
  "21" = "Coagulopathy",
  "22" = "Obesity",
  "23" = "Weight loss",
  "24" = "Fluid and electrolye disorders",
  "25" = "Blood loss anemia",
  "26" = "Deficiency anemias",
  "27" = "Alcohol abuse",
  "28" = "Drug abuse",
  "29" = "Psychoses",
  "30" = "Depression"
)

# Elixhauser with HTN combined:
comorb_list <- names_elix_htn
comorb_list["06b"] <- NULL
comorb_list["06a"] <- "Hypertension, combined"
names(comorb_list)[6] <- "06"

Comorbidity <- unlist(comorb_list)
Comorbidity <- as.data.frame(Comorbidity)

Comorbidity <- tibble::rownames_to_column(Comorbidity, "Abbreviation")
```

### **Calculate total patient counts by neuro status**

These counts will be used for Table 1 and determining denominator for comorbidity prevalence

```{r}
pt_counts <- read.csv('tables/site_pt_counts.csv') 

adult_count <- pt_counts %>% 
  filter(population == "Adult",
         !site == "BCH_results") %>% 
  mutate(None_n = sum(n_var_None, na.rm = TRUE),
         PNS_n = sum(n_var_Peripheral, na.rm = TRUE),
         CNS_n = sum(n_var_Central, na.rm = TRUE))

ped_count <- pt_counts %>% 
  filter(population == "Pediatric") %>% 
  mutate(None_n = sum(n_var_None, na.rm = TRUE),
         PNS_n = sum(n_var_Peripheral, na.rm = TRUE),
         CNS_n = sum(n_var_Central, na.rm = TRUE))

# combine adult and pediatric counts
neuro_pt_counts <- adult_count %>% 
  select(population, None_n, CNS_n, PNS_n) %>% 
  distinct() %>% 
  rbind(., ped_count %>% 
          select(population, None_n, CNS_n, PNS_n) %>% 
  distinct())

```

### **Abstract and process comorbidity data across healthcare systems**

```{r}
# create empty list to store comorbidities
comorb_table_list_adult <- list()
comorb_table_list_pediatric <- list()

## adults
for (i in sorted_sites[!sorted_sites %in% c("BCH_comorb_results", "GOSH_comorb_results")]) {
  tmp <- get(i)
  tmp_comorb <- tmp[[c(
    "first_hosp_results",
    "tableone_comorbidity_results",
    "comorbidity_neuro_adults"
  )]]
  tmp_comorb$site <- tmp[["site"]]
  comorb_table_list_adult[[i]] <- tmp_comorb %>%
    # because Elixhauser comorbidity index has two diabetes categories which capture the same diagnoses once we employ our truncation method, we will remove one of the diabetes categories
    filter(!Comorbidity == "Diabetes, uncomplicated") %>%
        mutate(Comorbidity = if_else(Comorbidity == "Diabetes, complicated", "Diabetes", Comorbidity),
              # rename hypertension
              Comorbidity = if_else(Comorbidity == "Hypertension, combined", "Hypertension", Comorbidity)) %>% 
    select(site, Comorbidity,  n_Total, n_None, n_Central, n_Peripheral)
}

## pediatrics
for (i in sorted_sites[!sorted_sites %in% c("VA1_comorb_results", "VA2_comorb_results", "VA3_comorb_results", "VA4_comorb_results", "VA5_comorb_results")]) {
  #print(i)
  tmp <- get(i)
  tmp_comorb <- tmp[[c(
    "first_hosp_results",
    "tableone_comorbidity_results",
    "comorbidity_neuro_pediatrics"
  )]]
  tmp_comorb$site <- tmp[["site"]]
  comorb_table_list_pediatric[[i]] <- tmp_comorb %>%
        # because Elixhauser comorbidity index has two diabetes categories which capture the same diagnoses once we employ our truncation method, we will remove one of the diabetes categories
    filter(!Comorbidity == "Diabetes, uncomplicated") %>%
        mutate(Comorbidity = if_else(Comorbidity == "Diabetes, complicated", "Diabetes", Comorbidity),
               # rename hypertension
               Comorbidity = if_else(Comorbidity == "Hypertension, combined", "Hypertension", Comorbidity)) %>% 
    select(site, Comorbidity,  n_Total, n_None, n_Central, n_Peripheral)
}

# combine all lists
comorb_table_adult <- comorb_table_list_adult %>% 
  bind_rows() %>% 
  mutate(population = "Adult")

comorb_table_pediatric <- comorb_table_list_pediatric %>% 
  bind_rows() %>% 
  mutate(population = "Pediatric")

comorb_table_all <- rbind(comorb_table_adult, comorb_table_pediatric)

# calculate total number of patients with each comorbidity across neurological status
comorb_table_wide <- comorb_table_all %>%
  data.frame() %>%
  left_join(., neuro_pt_counts, by = 'population') %>% 
  group_by(Comorbidity, population) %>%
  mutate(Comorb_Total = sum(n_Total, na.rm = TRUE),
         Comorb_Perc = round(Comorb_Total/(None_n + CNS_n + PNS_n)*100, 1),
         None_Total = sum(n_None, na.rm = TRUE),
         None_Perc = round(None_Total/None_n*100, 1),
         CNS_Total = sum(n_Central, na.rm = TRUE),
         CNS_Perc = round(CNS_Total/CNS_n*100, 1),
         PNS_Total = sum(n_Peripheral, na.rm = TRUE),
         PNS_Perc = round(PNS_Total/PNS_n*100, 1),
         `Comorb_N_%` = paste(Comorb_Total, "(", Comorb_Perc, "%)"),
         `NNC_N_%` = paste(None_Total, "(", None_Perc, "%)"),
         `CNS_N_%` = paste(CNS_Total, "(", CNS_Perc, "%)"),
         `PNS_N_%` = paste(PNS_Total, "(", PNS_Perc, "%)")) %>% 
  ungroup() %>%
  distinct(Comorbidity, population, Comorb_Total, None_Total, CNS_Total, PNS_Total,
           Comorb_Perc, None_Perc, CNS_Perc, PNS_Perc, `Comorb_N_%`, `NNC_N_%`, `CNS_N_%`, `PNS_N_%`)

comorb_table_plot <- comorb_table_wide %>%
  distinct(Comorbidity, population, Comorb_Total, `Comorb_N_%`, `NNC_N_%`, `CNS_N_%`, `PNS_N_%`)

datatable(comorb_table_plot %>% arrange(desc(Comorb_Total)), caption = "Number of Patients with each Pre-existing Comorbidity by Neurological Status")
```

**Save processed comorbidity data**

```{r}
write.csv(comorb_table_all, "processed/comorbidity_table_by_site.csv", row.names = FALSE)
write.csv(comorb_table_wide, "processed/comorbidity_table_cnps.csv", row.names = FALSE)
save(comorb_table_wide, file = "processed/comorbidity_table_cnps.rda")
save(neuro_pt_counts, file = "processed/neuro_pt_counts.rda")
```

