---
title: "Meta-Analysis"
output: html_document
---

Perform primary meta-analysis on Cox-PH models from each site.

```{r}
setwd("C:/Users/User/Box Sync/Projects/nu4ce/neuro/Phase2.1NeuroRSummaries/analysis_v2")
```


```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(metafor)
library(meta)
library(cowplot)
source("R/forester_custom.R")
source("R/analyze_survival.R")
```

# Import Data from each Healthcare system

```{r}
# read in files from results folder 
# this folder contains all of the local healthcare system level analyses
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}

rm(rdas, rda)

# create a list of participating healthcare systems from our study tracking spreadsheet
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"

# load site parameters
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

# filter the list of sites who ran the analysis
sorted_sites <- site_avails %>%
  filter(!is.na(date_v4_received)) %>%
  pull(siteid) %>%
  paste("results", sep = "_")

# list sites without race
sites_wo_race <- site_params %>%
  filter(!include_race) %>%
  pull(siteid)

# combine all rda files with 'results' in name
results <- mget(ls(pattern = "results"))

## read in pt counts
pt_counts_df <- read.csv('tables/site_pt_counts.csv')
```


## Define outcomes

```{r}
outcomes <-
  c(
    "time_first_discharge_reg_elix",
    "deceased_reg_elix"
  )
```


## Identify sites to include in the analysis

We will only include a site if they have >= 3 neuro patients

```{r}
sites_adult <- pt_counts_df %>% 
  filter(population == "Adult") %>% 
  mutate(neuro_sum = n_var_Central + n_var_Peripheral) %>% 
  filter(!neuro_sum < 3) %>% 
  distinct(site) %>% 
  mutate(site = gsub("_results", "", site))

sites_pediatric <- pt_counts_df %>% 
  filter(population == "Pediatric") %>% 
  mutate(neuro_sum = n_var_Central + n_var_Peripheral) %>% 
  filter(!neuro_sum < 3) %>% 
  distinct(site) %>% 
  mutate(site = gsub("_results", "", site))
```


## Get Cox model results - Adults

```{r}
cox_results_adults <- list()

for (outcome_i in outcomes) {
  cox_results_adults[[outcome_i]] <-
    results %>%
    lapply(get_cox_row, population = "adults", comorb_method = "ind", censor_cutoff = "90", outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}
```

## Get Cox model results - Pediatrics

```{r}
cox_results_pediatrics <- list()

for (outcome_i in outcomes) {
  cox_results_pediatrics[[outcome_i]] <-
    results %>%
    lapply(get_cox_row, population = "pediatrics", comorb_method = "ind", censor_cutoff = "90", outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}
```

## Random effects meta-analysis - CNS

set sm = "HR" when estimate is logHR (which is coef in our model): https://cran.r-project.org/web/packages/meta/meta.pdf - (search logHR in cran to see example)

*Note: We excluded sites with < 3 neuro patients in a category

```{r}
## adults 
meta_results_adults_cns <- list()

for (outcome_i in outcomes) {
  meta_results_adults_cns[[outcome_i]] <-
    cox_results_adults[[outcome_i]] %>%
    filter(site %in% sites_adult$site) %>% 
    bind_rows() %>%
    data.frame() %>%
    filter(variable == "neuro_postCentral") %>%
    metagen(
      TE = coef,
      seTE = se.coef.,
      data = .,
      sm = "HR", # hazard ratios
      comb.random = TRUE,
      comb.fixed = FALSE,
      method.tau = "DL", # default tau method
      hakn = FALSE,
      prediction = TRUE,
      studlab = site
    )
}

## pediatrics
meta_results_pediatrics_cns <- list()

for (outcome_i in outcomes) {
  meta_results_pediatrics_cns[[outcome_i]] <-
    cox_results_pediatrics[[outcome_i]] %>%
    filter(site %in% sites_pediatric$site) %>% 
    bind_rows() %>%
    data.frame() %>%
    filter(variable == "neuro_postCentral") %>%
    metagen(
      TE = coef,
      seTE = se.coef.,
      data = .,
      sm = "HR", # hazard ratios
      comb.random = TRUE,
      comb.fixed = FALSE,
      method.tau = "DL", # default tau method
      hakn = FALSE,
      prediction = TRUE,
      studlab = site
    )
}
```

## Random effects meta-analysis - PNS


```{r}
## adults
meta_results_adults_pns <- list()

for (outcome_i in outcomes) {
  meta_results_adults_pns[[outcome_i]] <-
    cox_results_adults[[outcome_i]] %>%
    filter(site %in% sites_adult$site) %>% 
    bind_rows() %>%
    data.frame() %>%
    filter(variable == "neuro_postPeripheral") %>%
    metagen(
      TE = coef,
      seTE = se.coef.,
      data = .,
      sm = "HR", # hazard ratios
      comb.random = TRUE,
      comb.fixed = FALSE,
      method.tau = "DL", # default tau method
      hakn = FALSE,
      prediction = TRUE,
      studlab = site
    )
}

## pediatrics
meta_results_pediatrics_pns <- list()

for (outcome_i in outcomes) {
  meta_results_pediatrics_pns[[outcome_i]] <-
    cox_results_pediatrics[[outcome_i]] %>%
    filter(site %in% sites_pediatric$site) %>% 
    bind_rows() %>%
    data.frame() %>%
    filter(variable == "neuro_postPeripheral") %>%
    metagen(
      TE = coef,
      seTE = se.coef.,
      data = .,
      sm = "HR", # hazard ratios
      comb.random = TRUE,
      comb.fixed = FALSE,
      method.tau = "DL", # default tau method
      hakn = FALSE,
      prediction = TRUE,
      studlab = site
    )
}

```

## Format meta results

```{r}
# cns
meta_results_adults_cns_df <- format_meta(meta_results_adults_cns)
meta_results_pediatrics_cns_df <- format_meta(meta_results_pediatrics_cns)

# pns
meta_results_adults_pns_df <- format_meta(meta_results_adults_pns)
meta_results_pediatrics_pns_df <- format_meta(meta_results_pediatrics_pns)
```

### save weights to generate the survival curves

4.1.2.1 Estimators of the Between-Study Heterogeneity:
https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pooling-es.html

> "inverse of the variance is used to determine the weight of each study"
>
> * *where "study" in our analysis is the healthcare system*
>
> For random effects, the calculation is performed by calculating an adjusted random-effects weight 
w∗k for each observation. Where k is the healthcare system

$w^*_k = \frac{1}{s^2 + tau^2}$ 


```{r}
# adult weights
save_weights(meta_results_df = meta_results_adults_cns_df,
             population = "adults", 
             comorb_method = "lpca", 
             censor_cutoff = "60", 
             cns_pns = "CNS")

save_weights(meta_results_df = meta_results_adults_pns_df,
             population = "adults", 
             comorb_method = "lpca", 
             censor_cutoff = "60", 
             cns_pns = "PNS")

save_weights(meta_results_df = meta_results_adults_cns_df,
             population = "adults", 
             comorb_method = "ind", 
             censor_cutoff = "90", 
             cns_pns = "CNS")

save_weights(meta_results_df = meta_results_adults_pns_df,
             population = "adults", 
             comorb_method = "ind", 
             censor_cutoff = "90", 
             cns_pns = "PNS")

# pediatric weights
save_weights(meta_results_df = meta_results_pediatrics_cns_df,
             population = "pediatrics", 
             comorb_method = "lpca", 
             censor_cutoff = "60", 
             cns_pns = "CNS")

save_weights(meta_results_df = meta_results_pediatrics_pns_df,
             population = "pediatrics", 
             comorb_method = "lpca", 
             censor_cutoff = "60", 
             cns_pns = "PNS")


save_weights(meta_results_df = meta_results_pediatrics_cns_df,
             population = "pediatrics", 
             comorb_method = "ind", 
             censor_cutoff = "90", 
             cns_pns = "CNS")

save_weights(meta_results_df = meta_results_pediatrics_pns_df,
             population = "pediatrics", 
             comorb_method = "ind", 
             censor_cutoff = "90", 
             cns_pns = "PNS")
```

**Prepare data for forest plots**

```{r}
# adults
meta_results_adults_cns_df_forest = prepare_data_forest_plots(meta_results_adults_cns_df)
meta_results_adults_pns_df_forest = prepare_data_forest_plots(meta_results_adults_pns_df)

# pediatrics
meta_results_pediatrics_cns_df_forest = prepare_data_forest_plots(meta_results_pediatrics_cns_df)
meta_results_pediatrics_pns_df_forest = prepare_data_forest_plots(meta_results_pediatrics_pns_df)
```

create a scale function to identify the min and max CI for each site, excluding sites with values of 'Inf' or our invalid sites

```{r}
scale_plot <- function(meta_results_df_forest, site_exclude = NULL) {
  scale <- meta_results_df_forest %>%
    filter(
      !Site %in% site_exclude,
      #!analysis %in% invalid_sites,
      !CI.Low == "Inf",
      !CI.High == "Inf"
    ) %>%
    mutate(
      min_est = min(CI.Low, na.rm = TRUE) - 1,
      max_est = max(CI.High, na.rm = TRUE) + 1,
      min_est = if_else(min_est + 1 >= -1, min(CI.Low, na.rm = TRUE)-0.1, min_est),
      min_est = if_else(min_est > 1, 0.5, min_est),
      max_est = if_else(max_est - 1 < 1, 1.1, max_est)) %>%
    distinct(min_est, max_est)

  return(scale)
}
```

#  Adults

### **CNS - Adults: Time to First Discharge**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

length_stay_first_results <- meta_results_adults_cns_df_forest %>%
  slice(grep(paste("time_first_discharge_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(length_stay_first_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(length_stay_first_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(length_stay_first_results, site_exclude = c("ICSM"))

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p1 <- forester(
  left_side_data = length_stay_first_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = length_stay_first_results$`Hazard Ratio`,
  ci_low = length_stay_first_results$CI.Low,
  ci_high = length_stay_first_results$CI.High,
  right_side_data = length_stay_first_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_adult_cns_discharge.png")))

p1
```

### **CNS - Adults: Time to mortality**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_adults_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

deceased_results <- meta_results_adults_cns_df_forest %>%
  slice(grep(paste("deceased_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(deceased_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(deceased_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(deceased_results, site_exclude = c("ICSM"))

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p2 <- forester(
  left_side_data = deceased_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = deceased_results$`Hazard Ratio`,
  ci_low = deceased_results$CI.Low,
  ci_high = deceased_results$CI.High,
  right_side_data = deceased_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_adult_cns_mortality.png")))

p2
```

### **PNS - Adults: Time to First Discharge**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

length_stay_first_results <- meta_results_adults_pns_df_forest %>%
  slice(grep(paste("time_first_discharge_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(length_stay_first_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(length_stay_first_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(length_stay_first_results, site_exclude = c("ICSM"))

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p3 <- forester(
  left_side_data = length_stay_first_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = length_stay_first_results$`Hazard Ratio`,
  ci_low = length_stay_first_results$CI.Low,
  ci_high = length_stay_first_results$CI.High,
  right_side_data = length_stay_first_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_adult_pns_discharge.png")))

p3
```

### **PNS - Adults: Time to mortality**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_adults_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

deceased_results <- meta_results_adults_pns_df_forest %>%
  slice(grep(paste("deceased_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(deceased_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(deceased_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(deceased_results, site_exclude = c("ICSM"))

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p4 <- forester(
  left_side_data = deceased_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = deceased_results$`Hazard Ratio`,
  ci_low = deceased_results$CI.Low,
  ci_high = deceased_results$CI.High,
  right_side_data = deceased_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_adult_pns_mortality.png")))

p4
```

# Pediatrics

### **CNS - Pediatrics: Time to First Discharge**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

length_stay_first_results <- meta_results_pediatrics_cns_df_forest %>%
  slice(grep(paste("time_first_discharge_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(length_stay_first_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(length_stay_first_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(length_stay_first_results, site_exclude = "BCH")

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p5 <- forester(
  left_side_data = length_stay_first_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = length_stay_first_results$`Hazard Ratio`,
  ci_low = length_stay_first_results$CI.Low,
  ci_high = length_stay_first_results$CI.High,
  right_side_data = length_stay_first_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_pediatric_cns_discharge.png")))

p5
```

### **CNS - Pediatrics: Time to mortality**

**HR too large**

```{r eval=FALSE, fig.width=8, message=FALSE, warning=FALSE, include=TRUE}
te.random = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_pediatrics_cns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

deceased_results <- meta_results_pediatrics_cns_df_forest %>%
  slice(grep(paste("deceased_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(deceased_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(deceased_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(deceased_results, site_exclude = "BCH")

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p6 <- forester(
  left_side_data = deceased_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = deceased_results$`Hazard Ratio`,
  ci_low = deceased_results$CI.Low,
  ci_high = deceased_results$CI.High,
  right_side_data = deceased_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_pediatric_cns_mortality.png")))

p6
```

### **CNS - Pediatrics: Time to First Discharge**

```{r fig.width=8, message=FALSE, warning=FALSE}
te.random = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "time_first_discharge_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

length_stay_first_results <- meta_results_pediatrics_pns_df_forest %>%
  slice(grep(paste("time_first_discharge_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(length_stay_first_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(length_stay_first_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(length_stay_first_results, site_exclude = "BCH")

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p7 <- forester(
  left_side_data = length_stay_first_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = length_stay_first_results$`Hazard Ratio`,
  ci_low = length_stay_first_results$CI.Low,
  ci_high = length_stay_first_results$CI.High,
  right_side_data = length_stay_first_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_pediatric_pns_discharge.png")))

p7
```

### **CNS - Pediatrics: Time to mortality**

**HR too large - cannot run**

```{r eval=FALSE, fig.width=8, message=FALSE, warning=FALSE, include=TRUE}
te.random = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(TE.random) %>% 
  as.numeric() %>% 
  round(.,2)

te.random.ci_lower = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(lower.random) %>% 
  as.numeric() 

te.random.ci_upper = meta_results_pediatrics_pns_df_forest %>% 
  filter(analysis == "deceased_reg_elix") %>% 
  distinct(upper.random) %>% 
  as.numeric() 

deceased_results <- meta_results_pediatrics_pns_df_forest %>%
  slice(grep(paste("deceased_reg_elix", collapse = "|"), analysis)) %>% 
  #add_row(.before = 1) %>%
  add_row(.after = nrow(.)) %>% 
  mutate(Site = ifelse(is.na(Site), "Effect size", Site),
         `Hazard Ratio` = ifelse(is.na(`Hazard Ratio`), round(te.random, 2), `Hazard Ratio`),
         `p-value` = ifelse(`p-value` < 0.001, "< .001*", round(`p-value`, 3))) %>% 
  fill(`p-value`, .direction = "down") %>% 
  mutate(`p-value` = ifelse(Site == "Effect size", `p-value`, ""),
         CI.Low = ifelse(Site == "Effect size", te.random.ci_lower, CI.Low),
         CI.High = ifelse(Site == "Effect size", te.random.ci_upper, CI.High),
         `Hazard Ratio ` = paste(`Hazard Ratio`, '(', CI.Low, ',', CI.High, ')'))


## define forest plot shapes
# shape #16 is normal circle; #18 is diamond
shapes <- rep(16, times = nrow(deceased_results))
shapes[length(shapes)] <- 18
sizes <- rep(3.25, times = nrow(deceased_results))
sizes[length(sizes)] <- 5
scale <- scale_plot(deceased_results, site_exclude = "BCH")

# note: `Hazard Ratio ` with confidence intervals has an extra space and used by `right_side_data` param
p8 <- forester(
  left_side_data = deceased_results %>% 
    select(Site) %>% 
    rename("Healthcare System" = "Site"),
  estimate = deceased_results$`Hazard Ratio`,
  ci_low = deceased_results$CI.Low,
  ci_high = deceased_results$CI.High,
  right_side_data = deceased_results[, c("Hazard Ratio ", "p-value")],
  display = TRUE,
  nudge_x = .5,
  font_family = "arial",
  arrows = TRUE,
  arrow_labels = c("Decreased Risk", "Increased Risk"),
  null_line_at = 1,
  xlim = c(scale$min_est, scale$max_est),
  #xbreaks = c(scale$min_est, 1, scale$max_est),
  point_sizes = sizes,
  point_shapes = shapes,
  file_path = here::here(paste0("figures/forestplot_pediatrics_pns_mortality.png")))

p8
```
