---
title: "meta-survival-curves"
author: "Meg Hutch"
date: "12/8/2021"
output: html_document
---

Generate survival curves

```{r}
setwd("C:/Users/User/Box Sync/Projects/nu4ce/neuro/Phase2.1NeuroRSummaries/analysis_v2")
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(metafor)
library(meta)
library(egg)
source("R/forester_custom.R")
source("R/analyze_survival.R")
```

# Import Data from each Healthcare system

```{r}
# read in files from results folder 
# this folder contains all of the local healthcare system level analyses
rdas <- list.files(
  path = "results",
  pattern = ".rda",
  full.names = TRUE
)
for (rda in rdas) {
  load(rda)
}

rm(rdas, rda)

# create a list of participating healthcare systems from our study tracking spreadsheet
site_google_url <- "https://docs.google.com/spreadsheets/d/1epcYNd_0jCUMktOHf8mz5v651zy1JALD6PgzobrGWDY/edit?usp=sharing"

# load site parameters
site_params <- googlesheets4::read_sheet(site_google_url, sheet = 1)
site_avails <- googlesheets4::read_sheet(site_google_url, sheet = 2)

# filter the list of sites who ran the analysis
sorted_sites <- site_avails %>%
  filter(!is.na(date_v4_received)) %>%
  pull(siteid) %>%
  paste("results", sep = "_")

# list sites without race
sites_wo_race <- site_params %>%
  filter(!include_race) %>%
  pull(siteid)

# combine all rda files with 'results' in name
results <- mget(ls(pattern = "results"))
```

## Define outcomes

```{r}
outcomes <-
  c(
    "time_first_discharge_reg_elix",
    "deceased_reg_elix"
  )
```

## Exclusion of sites

```{r}
results[["BCH_results"]] <- NULL
results[["GOSH_results"]] <- NULL
results[["NUH_results"]] <- NULL
results[["UKFR_results"]] <- NULL
```


## Get Cox model results - Adults

```{r}
cox_results_adults <- list()

for (outcome_i in outcomes) {
  cox_results_adults[[outcome_i]] <-
    results %>%
    lapply(get_cox_row, population = "adults", comorb_method = "ind", censor_cutoff = "90", outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}
```

## Get adjusted KM results - Adults

```{r}
## Get Cox model results - Adults

km_results_adults <- list()

for (outcome_i in outcomes) {
  km_results_adults[[outcome_i]] <-
    results %>% 
    lapply(get_km_row, population = "adults", comorb_method = "ind", censor_cutoff = "90", outcome = outcome_i) %>%
    bind_rows() %>%
    mutate(outcome = outcome_i)
}
```

```{r}
res_dat_surv <- bind_rows(km_results_adults) %>%
  # cbind(., res_dat[c("time", "site", "outcome")]) %>% 
  # pivot_longer(cols = None:CNS,  names_to = "strata", values_to = "surv") %>% 
  # left_join(., res_dat_std.err) %>%
  # left_join(., res_dat_lower) %>% 
  # left_join(., res_dat_upper) %>% 
  # mutate(std.err = ifelse(is.nan(std.err), NA, std.err)) %>%
  # filter(!time < 0) %>% 
  add_count(site, strata, outcome, name = "n_timepoints") %>%
  complete(time, site, nesting(strata, outcome)) %>%
  #mutate(surv = if_else(is.na(surv) & time == 0, 1, surv)) %>%
  group_by(site, strata, outcome) %>%
  arrange(time) %>% 
  fill(surv, .direction = "down") %>%
  fill(std.err.sqrt, n_timepoints, .direction = "down") %>%
  fill(std.err, n_timepoints, .direction = "down") %>%
  #fill(lower, .direction = "down") %>%
  #fill(upper, .direction = "down") %>%
  #fill(std.err, n_site, n_timepoints, .direction = "downup") %>%
  #filter(n_timepoints >= 5, time >= 0) %>%
  ungroup()
```

### Evaluate survival curves by site

```{r}
res_dat_surv$strata <- toupper(res_dat_surv$strata)
res_dat_surv$strata <- as.factor(res_dat_surv$strata)
res_dat_surv$strata <- fct_recode(res_dat_surv$strata, "NNC" = "NONE")

res_dat_surv$strata <- factor(res_dat_surv$strata, levels=c("NNC", "CNS", "PNS"), labels=c("NNC", "CNS", "PNS"))

#group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")
group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato")

site_names <- names(results) %>% 
  gsub("_results", "", .)

# calculate CIs
zval <- qnorm(1- (1-0.95)/2, 0, 1)
standard_error <- function(x) sd(x, na.rm = TRUE) / sqrt(length(x)) # Create own function
```

```{r}
pdf(file="figures/site_level_survival_curves.pdf", height = 5, width = 6)  

for(i in site_names) {
  
  plot <- res_dat_surv %>%
    mutate(outcome = factor(outcome, levels = outcomes) %>%
             fct_recode(
               "Mortality" = "time_deceased_reg_elix",
               "Discharge" = "time_first_discharge_reg_elix"
             )) %>% 
    filter(site == i) %>% 
     group_by(outcome, strata) %>%
     mutate(
       ci_lower = surv - zval*std.err.sqrt, 
       ci_upper = surv + zval*std.err.sqrt) %>% 
       #lt_hat = log(-log(surv)),
       #se_lt_hat = standard_error(lt_hat)) %>%
     ungroup() %>%
     # mutate(ci_lower = exp(-exp(log(-log(surv)) + zval*se_lt_hat)),
     #        ci_upper = exp(-exp(log(-log(surv)) - zval*se_lt_hat))) %>%
    # filter(time <= 60) %>% 
    ggplot(aes(
    x = time, y = surv,
    color = strata,
    fill = strata,
  )) +
  geom_line(aes()) +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper, fill = strata), alpha = 0.2, linetype = 0, show.legend = FALSE) + 
  labs(color = NULL, y = NULL) +
  scale_colour_manual(values = group.colors) + 
  scale_fill_manual(values = group.colors) + 
  facet_wrap(~outcome, ncol = 3) +
  coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
  xlab("Time (days)") + 
  ylab("Event Probability") +
  theme_classic() + 
  labs(color = "Neuro Status",
       fill = "") + 
  theme(legend.position="top")
  
  print(plot + ggtitle(paste(i)) + 
           theme(plot.title = element_text(hjust = 0.5)))
  
  
}

dev.off()

```

### Weight each site 

Here we will weight each site by the inverse of its variance calculated from the CNS and PNS meta-analysis models. We will take the average of the CNS and PNS weights

```{r}
#load("survival_model/adults_lpca_60_CNS.rda")
#load("survival_model/adults_lpca_60_PNS.rda")

load("survival_model/adults_ind_90_CNS.rda")
load("survival_model/adults_ind_90_PNS.rda")

# rename weight column
cns_weights <- adults_ind_90_CNS %>% 
  rename("cns_weight" = Weight.random) %>% 
  select(-strata)

pns_weights <- adults_ind_90_PNS %>% 
  rename("pns_weight" = Weight.random) %>% 
  select(-strata) 

## average the weights
avg_weights <- cns_weights %>% 
  left_join(., pns_weights, by = c("analysis", "studlab")) %>% 
  mutate(cns_weight = as.numeric(cns_weight),
         pns_weight = as.numeric(pns_weight),
         avg_weight = rowMeans(cbind(cns_weight, pns_weight), na.rm = TRUE)) %>% 
  rename("outcome" = analysis,
         "site" = studlab)
```

### Generate survival curves

```{r}
#chuan's code

## y is the vector of beta coefficients; 
## s is the vector of SE of beta coefficients;
## wt is the weight (e.g, number of events, make sure it does not change over time)

# Meg added the rule to handle cases when v.between is a negative number based on the following reference which explains: 
#https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/heterogeneity.html
# the value of I2 cannot be lower than 0%, so if Q happens to be smaller than K-1, we simply use 0 instead of a negative value.
metaFUN.randomeffect=function(y, s, wt){
  mm=c(y%*%wt/sum(wt))
  df=length(y)-1
  C=sum(wt)-sum((wt)^2)/sum(wt)
  Q=wt%*%(y-mm)^2
  k = length(y)
  if (Q < k-1) {
  v.between=0
} else {
  v.between=c((Q-df)/C); v.between # variance between (tau^2)
}
  ww=1/(s^2+v.between) # random-effects weight
  ss=sqrt(1/sum(ww)) # sum of squares 
  ## MH addition based o link above and discussion of T^2 approximating X^2 distribution## 
  ci_low = qchisq(0.025, df=df)
  ci_high = qchisq(0.975, df=df)
  data.frame(pool_mean=mm, pool_se=ss, pool_low = ci_low, pool_high = ci_high)
}

zval <- qnorm(1- (1-0.95)/2, 0, 1)

meta_surv_df <- res_dat_surv %>%
  left_join(., avg_weights, by = c("site", "outcome")) %>%
  ungroup() %>%  
  as.data.frame() %>% 
  filter(!is.na(surv)) %>% 
  #group_by(site, strata, outcome) %>% 
  # mutate(lt_hat = log(-log(surv))) %>% 
  # filter(!is.infinite(lt_hat)) %>% 
  # mutate(se_lt_hat = standard_error(lt_hat)) %>% 
  group_by(strata, outcome, time) %>%
  mutate(
    outcome = factor(outcome, levels = outcomes) %>%
      fct_recode(
        "Mortality" = "deceased_reg_elix",
        "Discharge" = "time_first_discharge_reg_elix"
      ),
    strata = str_replace(strata, "neuro_post=", ""),
    surv = metaFUN.randomeffect(surv, std.err.sqrt, avg_weight)$pool_mean,
    se = metaFUN.randomeffect(surv, std.err.sqrt, avg_weight)$pool_se,
    ci_low = metaFUN.randomeffect(surv, std.err, avg_weight)$pool_low,
    ci_high = metaFUN.randomeffect(surv, std.err, avg_weight)$pool_high,
    ci_l = surv - se*zval,
    ci_u = surv + se*zval) %>% 
  ungroup() %>% 
  # group_by(strata, outcome) %>% 
  #   mutate(
  #      lt_hat = log(-log(surv)),
  #      se_lt_hat = standard_error(lt_hat),
  #      ci_low = surv - se_lt_hat*zval,
  #     ci_up = surv + se_lt_hat*zval) %>% 
  distinct(outcome, strata, time, surv, se, ci_l, ci_u, ci_low, ci_high) 

# refactor
meta_surv_df$strata <- as.factor(meta_surv_df$strata)

meta_surv_df$strata <- factor(meta_surv_df$strata, 
                              levels=c("NNC", "CNS", "PNS"),
                              labels=c("NNC", "CNS", "PNS"))

#group.colors <- c(NNC = "darkgray", PNS = "#d90429", CNS ="#ff9c8b") #survival_curves1.2
group.colors <- c(NNC = "darkgray", PNS = "slateblue", CNS ="tomato") 

surv_curves <- meta_surv_df %>%
  ggplot(aes(
    x = time, y = surv,
    color = strata,
    fill = strata,
  )) +
  geom_line(aes()) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high, fill = strata), alpha = 0.2, linetype = 0, show.legend = FALSE) + 
  labs(color = NULL, y = NULL) +
  scale_colour_manual(values = group.colors) + 
  scale_fill_manual(values = group.colors) + 
  facet_wrap(~outcome, ncol = 3) +
coord_cartesian(clip = "off", ylim = c(0, 1), expand = FALSE) +
  xlab("Time (days)") + 
  ylab("Event Probability") +
  scale_x_continuous(limits = c(1, 90), breaks = c(1, 30, 60, 90)) +
  theme_classic() + 
  labs(color = "Neuro Status",
       fill = "") + 
  theme(legend.position="top",
        strip.text = element_text(color = "black", size = 12)); surv_curves

ggsave("figures/survival_curves.png", surv_curves, height = 5, width = 6)

# confidence interval too narrow?
View(meta_surv_df %>% mutate(ci_diff = abs(ci_l - ci_u)))
```

```{r}

```

